---
title: "p8105_hw6_ps3194"
author: "Pangsibo Shen"
date: "12/5/2020"
output: html_document
---
```{r message=FALSE}
library(tidyverse)
library(modelr)
library(p8105.datasets)
library(broom)
```

## Problem 1

```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>%
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
    ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != c("Tulsa, AL")
    ) %>%
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```

Start with one city.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")

glm(resolution ~ victim_age + victim_race + victim_sex,
    data = baltimore_df,
    family = binomial()) %>%
  broom::tidy() %>%
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>%
  select(term, OR, starts_with("CI")) %>%
  knitr::kable(digits = 3)
```

Try this across cities.

```{r}
models_results_df = 
  homicide_df %>%
  nest(data = -city_state) %>%
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>%
  select(city_state, results) %>%
  unnest(results) %>%
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>%
  select(city_state, term, OR, starts_with("CI"))
```



```{r}
models_results_df %>%
  filter(term == "victim_sexMale") %>%
  mutate(city_state = fct_reorder(city_state,OR)) %>%
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

## Problem 2

```{r}
birthweight_df = 
  read_csv("data/birthweight.csv") %>%
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
  ) %>%
  relocate(bwt, .after = wtgain)
```
```{r}
# Fit a regression using all predictors
mult_fit = lm(bwt ~., data = birthweight_df)
summary(mult_fit)
```

For the MLR variable selection process, we are going to implement backward elimination which takes out non-significant variables 'one at a time' starting with the highest p-value.
```{r}
# backward elimination
step(mult_fit, direction = 'backward')
```

After the backward elimination, we ended up with a new model below:
```{r}
fit_be = lm(formula = bwt ~ babysex + bhead + blength + delwt + fincome + 
    gaweeks + mheight + mrace + parity + ppwt + smoken, data = birthweight_df)
summary(fit_be)

fit_model =  lm(formula = bwt ~ babysex + bhead  + blength + wtgain + gaweeks + mheight + mrace + parity  + smoken, data = birthweight_df)
summary(fit_model)
```

After reviewed the summary of the model after backward elimination, we took additional step to drop the fincome since its p-value is greater than 0.05. We also removed delwt and ppwt and added wtgain which is delwt - ppwt. Finally, we got the fit_model as the proposed model.


```{r}
# Diagnostics
birthweight_df %>% 
  modelr::add_residuals(fit_model) %>% 
  modelr::add_predictions(fit_model) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point() +
  xlab("Predicted/Fitted value") +
  ylab("Residual") +
  ggtitle("Residual vs Fitted Values Plot") +
  geom_hline(yintercept=00, linetype = "dashed", color = "red")
```

now, let's construct the other two models provided by the prompt!
```{r}
fit_p1 = lm(formula = bwt ~ blength + gaweeks, data = birthweight_df)
tidy(fit_p1)
fit_p2 = lm(formula = bwt ~ babysex*bhead*blength, data = birthweight_df)
tidy(fit_p2)
```

```{r}
cv_df = 
  crossv_mc(birthweight_df, 100) %>%
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )
```

```{r}
cv_df = 
  cv_df %>% 
  mutate(
    fit_model = map(.x = train, ~ lm(formula = bwt ~ babysex + bhead  + blength + wtgain + gaweeks + mheight + mrace + parity  + smoken, data = .x)),
    fit_p1 = map(.x = train, ~ lm(formula = bwt ~ blength + gaweeks, data = .x)),
    fit_p2 = map(.x = train, ~ lm(formula = bwt ~ babysex*bhead*blength, data = .x))
  ) %>% 
  mutate(
    rmse_model = map2_dbl(.x = fit_model, .y = test, ~rmse(model = .x, data = .y)),
    rmse_p1 = map2_dbl(.x = fit_p1, .y = test, ~rmse(model = .x, data = .y)),
    rmse_p2 = map2_dbl(.x = fit_p2, .y = test, ~rmse(model = .x, data = .y))
  )
```

```{r}
#calculate mean prediction error across three models
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  group_by(model) %>% 
  summarize(avg_rmse = mean(rmse))
```

```{r}
#plot the mean prediction error density across three models
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin()
```

## Porblem 3
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
weather_bootstrap = 
  weather_df %>%
  modelr::bootstrap(5000, id = "strap_number") %>%
  mutate(
    models = map(.x = strap, ~lm(tmax ~tmin, data = .x)), 
    results = map(models, broom::tidy),
    glance = map(models, broom::glance)
  ) %>%
  select(strap_number, results, glance)
```

```{r}
#Plot the distribution of r squared
weather_bootstrap %>%
  unnest(glance) %>%
  ggplot(aes(r.squared)) +
  geom_density()


r_squared = 
  weather_bootstrap %>%
  unnest(glance) %>%
  select(r.squared) %>%
  unlist()

#construct 95% CI for r squared
r_squared_CI = 
  tibble(
    mean = mean(r_squared),
    ci_lower = quantile(r_squared, 0.025),
    ci_upper = quantile(r_squared, 0.975)
    )

r_squared_CI
```

```{r}
#Plot the distribution of log(intercept*beta1)
weather_bootstrap %>%
  unnest(results) %>%
  select(strap_number, term, estimate) %>%
  pivot_wider(names_from  = term, values_from = estimate) %>%
  rename(intercept = '(Intercept)') %>%
  mutate(estimate = log10(intercept*tmin)) %>%
  ggplot(aes(estimate)) +
  geom_density()

log_betas = 
  weather_bootstrap %>%
  unnest(results) %>%
  select(strap_number, term, estimate) %>%
  pivot_wider(names_from  = term, values_from = estimate) %>%
  rename(intercept = '(Intercept)') %>%
  mutate(estimate = log10(intercept*tmin)) %>%
  select(estimate) %>%
  unlist()

#construct 95% CI for log(intercept*beta1)
log_betas_CI = 
  tibble(
    mean = mean(log_betas),
    ci_lower = quantile(log_betas, 0.025),
    ci_upper = quantile(log_betas, 0.975)
    )

log_betas_CI
```






