---
title: "p8105_hw6_ps3194"
author: "Pangsibo Shen"
date: "12/5/2020"
output: html_document
---
```{r message=FALSE}
library(tidyverse)
library(modelr)
library(p8105.datasets)
library(broom)
```

## Problem 1

```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>%
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
    ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != c("Tulsa, AL")
    ) %>%
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```

Start with one city.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")

glm(resolution ~ victim_age + victim_race + victim_sex,
    data = baltimore_df,
    family = binomial()) %>%
  broom::tidy() %>%
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>%
  select(term, OR, starts_with("CI")) %>%
  knitr::kable(digits = 3)
```

Try this across cities.

```{r}
models_results_df = 
  homicide_df %>%
  nest(data = -city_state) %>%
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>%
  select(city_state, results) %>%
  unnest(results) %>%
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>%
  select(city_state, term, OR, starts_with("CI"))
```



```{r}
models_results_df %>%
  filter(term == "victim_sexMale") %>%
  mutate(city_state = fct_reorder(city_state,OR)) %>%
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

## Problem 2

```{r}
birthweight_df = 
  read_csv("data/birthweight.csv") %>%
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
  ) %>%
  relocate(bwt, .after = wtgain)
```
```{r}
# Fit a regression using all predictors
mult_fit = lm(bwt ~., data = birthweight_df)
summary(mult_fit)
```

For the MLR variable selection process, we are going to implement backward elimination which takes out non-significant variables 'one at a time' starting with the highest p-value.
```{r}
# backward elimination
step(mult_fit, direction = 'backward')
```

After the backward elimination, we ended up with a new model below:
```{r}
fit_be = lm(formula = bwt ~ babysex + bhead + blength + delwt + fincome + 
    gaweeks + mheight + mrace + parity + ppwt + smoken, data = birthweight_df)
summary(fit_be)

fit_model =  lm(formula = bwt ~ babysex + bhead  + blength + wtgain + gaweeks + mheight + mrace + parity  + smoken, data = birthweight_df)
summary(fit_model)
```

After reviewed the summary of the model after backward elimination, we took additional step to drop the fincome since its p-value is greater than 0.05. We also removed delwt and ppwt and added wtgain which is delwt - ppwt. Finally, we got the fit_model as the proposed model.

## Diagnostics

```{r}
birthweight_df %>% 
  modelr::add_residuals(fit_model) %>% 
  modelr::add_predictions(fit_model) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point() +
  xlab("Predicted/Fitted value") +
  ylab("Residual") +
  ggtitle("Residual Plot for Y (baby’s birth weight)") +
  geom_hline(yintercept=00, linetype = "dashed", color = "red")
```



